Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-21 NEUROC/sec3-experiment-design.tex
粗略修改了Q1

@@

@@

    \item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})

          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affect the training time per epoch and the peak memory usage during training.
          %
          To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of the GPU) changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.

>>>>

% added by wangyupan, 2020-12-21 ----start----
In the precision experiment of hyper-parameters, we used the same training procedure for all the models. 
%
That is, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
same initialization (weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}. 
%
We trained for a maximum of 100k epochs. 
%
If total validation loss (loss on the data plus regularization loss) did not improve for 50 epochs, we would stop training. 
%
We reset the state of the weights of the step with the lowest validation loss and got the reported test accuracy.
%
Besides, in the precision experiment of sampling techniques, we selected the network structure corresponding to the highest accuracy in the hyperparameter experiment for each dataset of each model.
% added by wangyupan, 2020-12-21 ----end----

@@

% added by wangyupan, 2020-12-21 ----start----
In sampled-based inference experiment, according to \cite{weihua2020_ogb-benchmark}, we used neighbor sampler \cite{hamilton2017_graphsage} with batch size of 1024 and all neighbors were inclued in all layers.
% added by wangyupan, 2020-12-21 ----end----

@@

    \item[Q1] \emph{How do the hyper-parameters affect the training time, the memory usage, and the accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
          % TODO: 进一步修改
          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
          %
          The hyper-parameters affect the training time per epoch and the peak memory usage during training.
          %
          To evaluate their effects, we measured how the training time per epoch, the peak memory usage (of the GPU), and the accuracy changed as we increased the values of the hyper-parameters.
          %
          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
          %
          The complexity analysis allowed us to analyze performance bottlenecks theoretically.
